%-------------------------
% Resume in Latex
% Author : Frank Mathew Sajan
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

%----------FONT OPTIONS----------
\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins - AGGRESSIVE 1-PAGE FIT
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.6in}
\addtolength{\textheight}{1.25in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-8pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-6pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge \scshape Frank Mathew Sajan} \\ \vspace{2pt}
    \small Amaravati, India $|$ \href{mailto:frankmathewsajan@gmail.com}{\underline{frankmathewsajan@gmail.com}} $|$ 
    \href{https://linkedin.com/in/frankmathewsajan}{\underline{LinkedIn}} $|$
    \href{https://github.com/frankmathewsajan}{\underline{GitHub}} $|$
    \href{https://leetcode.com/u/frankmathewsajan/}{\underline{LeetCode}} $|$
    \href{https://itsfrank.web.app/}{\underline{Portfolio}}
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Vellore Institute of Technology}{Amaravati, India}
      {Bachelor of Technology in Computer Science, Specialization in AI/ML}{Sept. 2023 -- Jul. 2027}
      \vspace{1pt}
      \small{\item{
       \textbf{CGPA}: 8.62 / 10.00 \\
       \textbf{Coursework}: \textbf{Data Structures \& Algorithms}, OOP (Java/C++), DBMS (Normalization), OS (Concurrency)
      }}
  \resumeSubHeadingListEnd

%-----------TECHNICAL SKILLS (PIVOTED FOR DATA SCIENCE)-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Data Science \& ML}{: \textbf{Pandas, NumPy, Scikit-learn}, Deep Learning (Basic), Data Visualization (Matplotlib), RAG} \\
     \textbf{Languages}{: \textbf{Python}, \textbf{SQL}, C++, Java, JavaScript (ES6+)} \\
     \textbf{Core Concepts}{: Data Structures \& Algorithms, \textbf{Database Normalization}, System Design, OOP} \\
     \textbf{Frameworks}{: React.js, Django, FastAPI, TensorFlow/Keras (Exposure), REST APIs} \\
     \textbf{Tools \& Cloud}{: AWS (EC2, S3), Docker, Git/GitHub, VS Code, Supabase, Linux/Bash}
    }}
 \end{itemize}

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Founding Engineer \& Product Lead}{Aug 2025 -- Present}
      {House of Muziris (D2C Startup) $|$ \href{https://houseofmuziris.com}{\underline{Live Link}}}{Kerala, India}
      \resumeItemListStart
        \resumeItem{Architected a data-centric full-stack MVP using \textbf{React, Django, and PostgreSQL}, ensuring rigorous data validation for FSSAI compliance and supply chain tracking.}
        \resumeItem{Designed a normalized \textbf{database schema} to model complex inventory states, preventing data inconsistency and enabling accurate stock forecasting.}
        \resumeItem{Implemented analytics logging within the high-availability waitlist system to capture \textbf{user engagement metrics} during marketing campaigns.}
      \resumeItemListEnd

    \resumeSubheading
      {Software Engineering Intern}{Jun 2025 -- Jul 2025}
      {TechtoGreen Drone \& Robotics Pvt. Ltd. (IIEC Incubator) $|$ \href{https://medium.com/@frankmathewsajan}{\underline{Case Study}}}{Vijayawada, India}
      \resumeItemListStart
        \resumeItem{\textbf{Engineered the cloud inference pipeline} for a Deep Learning anomaly detection model on AWS EC2, implementing system observability via RESTful APIs.}
        \resumeItem{Analyzed flight path data to optimize autonomous drone control algorithms, resulting in a \textbf{30\% increase in field coverage efficiency}.}
        \resumeItem{Engineered a fault-tolerant \textbf{data transmission pipeline} using LoRa, achieving $>$99\% Packet Delivery Ratio (PDR) for critical telemetry datasets.}
      \resumeItemListEnd

    \resumeSubheading
      {Deputy Captain - Technical Research}{Sep 2023 -- Present}
      {IETE VIT-AP (Student Chapter)}{Amaravati, India}
      \resumeItemListStart
        \resumeItem{Mentoring 20+ student developers in technical research, fostering a culture of \textbf{data-driven experimentation} in Embedded Systems and IoT projects.}
        \resumeItem{Reviewing technical papers and IoT developments to drive innovation in student research initiatives.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{NASA Space Apps Challenge (Global Nominee)} $|$ \emph{React, Satellite Data API, AI}}{Oct 2024}
          \resumeItemListStart
            \resumeItem{Selected as a \textbf{Global Nominee (Top 1\% of 93,000+ participants)} for engineering an AI-driven tool utilizing \textbf{PACE satellite data}.}
            \resumeItem{Built a dynamic \textbf{Data Visualization dashboard} to simplify complex oceanographic datasets, making scientific data accessible to non-technical users.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{Rural School Management System} $|$ \emph{PostgreSQL, Supabase, Data Pipelines}}{Aug 2025 -- Nov 2025}
          \resumeItemListStart
            \resumeItem{Digitized academic records for 200+ students, establishing a structured \textbf{data pipeline} that reduced manual entry time by 15 hours/week.}
            \resumeItem{Optimized \textbf{SQL queries} for reporting modules, cutting data retrieval latency by 35\% on low-bandwidth networks.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd

%-----------CERTIFICATIONS & AWARDS-----------
\section{Certifications \& Awards}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Cloud/AI}: AWS Academy Graduate (Cloud Architecting), Oracle GenAI Certified Professional (2025) \\
     \textbf{Code}: CS50P: Programming with Python (Harvard, 2024), Automation Anywhere Essentials (2025) \\
     \textbf{Leadership}: McKinsey.org Forward Program (Problem Solving \& Leadership, 2025) \\
     \textbf{Awards}: Rajya Puraskar (State Award, Bharat Scouts \& Guides) -- Highest State Honor for Discipline.
    }}
 \end{itemize}

%-------------------------------------------
\end{document}